Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2017-06-26 paper/structureScene.tex
do not hyphenate nearest neighbor, rendered -> made

Many algorithms in pattern recognition, including nearest-neighbor classifiers and support vector machines (SVMs), tend to work best when all features follow a standard normal distribution across all training instances \cite{Hsu2003}.
Yet the distribution of the scattering coefficients is skewed towards larger values. We can reduce this skewness by applying a pointwise concave transformation to all coefficients. In particular, we find that the logarithm performs particularly well in this respect.
Figure \ref{fig:histograms} shows the distribution of an arbitrarily chosen scattering coefficient over the DCASE 2013 dataset, before and after logarithmic compression.

@@

A support vector machine (SVM) is a binary discriminative classifier that attempts to find a separating hyperplane between a pair of classes of that provides the maximal margin between the two sets \cite{Cortes1995}. From another point of view, it attempts to find a direction on which to project in order to maximize separation between two point clouds. Since it is not a generative, but discriminative model, it is able to pick out those feature vectors that best characterize a particular class of auditory scenes compared to another. This property, coupled with its ease of use and efficient implementations \cite{libsvm} have rendered SVMs a popular choice for many classification systems.

>>>>

Many algorithms in pattern recognition, including nearest neighbor classifiers and SVMs, tend to work best when all features follow a standard normal distribution across all training instances \cite{Hsu2003}.
Yet the distribution of the scattering coefficients is skewed towards larger values. We can reduce this skewness by applying a pointwise concave transformation to all coefficients. In particular, we find that the logarithm performs particularly well in this respect.
Figure \ref{fig:histograms} shows the distribution of an arbitrarily chosen scattering coefficient over the DCASE 2013 dataset, before and after logarithmic compression.

@@

A support vector machine (SVM) is a binary discriminative classifier that attempts to find a separating hyperplane between a pair of classes of that provides the maximal margin between the two sets \cite{Cortes1995}. From another point of view, it attempts to find a direction on which to project in order to maximize separation between two point clouds. Since it is not a generative, but discriminative model, it is able to pick out those feature vectors that best characterize a particular class of auditory scenes compared to another. This property, coupled with its ease of use and efficient implementations \cite{libsvm} have made SVMs a popular choice for many classification systems.
